The Argennon Virtual Machine

### 2021-03-18 tex/avm.tex
Make images a bit smaller
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Remove htm directory from git
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    %\includegraphics[width=17cm]{../img/Alg1.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
        {Txns}{$T$}
        \KwData{The execution dag $\Graph = (\Vertices,E)$ of a transaction set \Txns}
        \KwResult{The state of the AVM after applying \Txns with any ordering respecting \Graph}
        \BlankLine
        \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
        \While{$\Vertices \neq \varnothing$}
        {
            wait until a new free processor is available\;
            \If{the execution of a transaction was finished}
            {
                remove the vertex of the finished transaction \V from \Graph\;
                \For{each vertex $u \in Adj[\V]$}
                {
                    \If{$u$ has zero in degree}
                    {
                        $\Ready \gets \Ready \cup u$\;
                    }
                }
            }
            \If{$\Ready \neq \varnothing$}
            {
                remove a vertex from \Ready and assign it to a processor\;
            }
        }
        \caption{executing DAG transactions}\label{alg:exec_dag}
    \end{algorithm}

@@

    %\includegraphics[width=17cm]{../img/Alg2.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{Txns}{$T$}\SetKwData{Gd}{$G_d=(V_d,E_d)$}
        \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
        \Input{The memory dependency graph \Gd of a transaction set \Txns\\A proper coloring of $G_d$}
        \Output{An execution dag $G_e=(V_e,E_e)$ for the transaction set \Txns}
        \BlankLine
        $V_e \gets V_d$\;
        $E_e \gets \varnothing$\;
        define a total order on colors of $G_d$\;
        \For{each edge $\{u,v\} \in E_d$}
        {
            \eIf{$color[u] < color[v]$}
            {
                $E_e \gets E_e \cup (u,v)$\;
            }{
                $E_e \gets E_e \cup (v,u)$\;
            }
        }
        \caption{Constructing an execution DAG}\label{alg:gen_dag}
    \end{algorithm}

@@

    This problem can be easily solved by using a concurrent counter (CC) for storing the balance of this type of
    accounts. A concurrent counter is a data structure which improves concurrency by using multiple memory locations for
    storing a single counter. The value of the concurrent counter is equal to the sum of its sub counters and it can
    be incremented or decremented by incrementing/decrementing any of the sub counters. This way, a concurrent
    counter trades concurrency with memory usage.

    A pseudocode for implementing a concurrent counter (CC) which returns an error when the value of the counter
    becomes negative, follows:

    %\includegraphics[width=17cm]{../img/Alg3.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{CC}{Counter}
        \SetKwFunction{Inc}{Increment}\SetKwFunction{Dec}{Decrement}\SetKwFunction{AtomInc}{AtomicIncrement}
        \SetKwFunction{AtomDec}{AtomicDecrement}\SetKwFunction{AtomSet}{AtomicSet}
        \SetKwProg{Fn}{Function}{}{}
        \BlankLine
        \Fn{\Inc{\CC, value, seed}}
        {
            $i \gets seed \bmod \CC.size$\;
           \AtomInc{$\CC.cell[i]$, value}\;
        }
        \BlankLine
        \Fn{\Dec{\CC, value, seed, attempt}}
        {
            \If {attempt = \CC.size}
            {
                restore \CC by adding back the subtracted value\;
                \KwRet{Error}\;
            }
            $i \gets seed \bmod \CC.size$\;
            $i \gets (i + attempt) \bmod \CC.size$\;
            \eIf {$\CC.cell[i] \geq value$}
            {
                \AtomDec{$\CC.cell[i]$, value}\;
            }{
                $r \gets value - \CC.cell[i]$\;
                \AtomSet{$\CC.cell[i]$, $0$}\;
                \Dec{\CC, r, seed, $attempt + 1$}\;
            }
        }
        \caption{Concurrent counter}\label{alg:CC}
    \end{algorithm}

@@

    %\includegraphics[width=17cm]{../img/Alg4.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{V}{$v_0$}\SetKwData{Graph}{$G_e$}\SetKwData{Chunk}{$C_k$}\SetKwData{Txns}{$T$}
        \SetKwFunction{RPrune}{RecursivePrune}
        \SetKwProg{Fn}{Function}{}{}
        \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
        \Input{An execution dag and a memory chunk \Chunk}
        \Output{The pruned execution dag based on \Chunk}
        \BlankLine
        \For{each vertex \V with out degree $0$}
        {
            \RPrune{\V}\;
        }
        \BlankLine
        \Fn{\RPrune{\V}}
        {
            \If{$Adj[\V] = \varnothing$ {\bf and} \V does not modify \Chunk}
            {
                remove \V from \Graph\;
                \For{each $u$ such that $\V \in Adj[u]$}
                {
                    \RPrune{u}\;
                }
            }
        }
        \caption{Pruning the execution DAG}\label{alg:prune_dag}
    \end{algorithm}

>>>>

    %\includegraphics[width=17cm]{../img/Alg1s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
        {Txns}{$T$}
        \KwData{The execution dag $\Graph = (\Vertices,E)$ of a transaction set \Txns}
        \KwResult{The state of the AVM after applying \Txns with any ordering respecting \Graph}
        \BlankLine
        \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
        \While{$\Vertices \neq \varnothing$}
        {
            wait until a new free processor is available\;
            \If{the execution of a transaction was finished}
            {
                remove the vertex of the finished transaction \V from \Graph\;
                \For{each vertex $u \in Adj[\V]$}
                {
                    \If{$u$ has zero in degree}
                    {
                        $\Ready \gets \Ready \cup u$\;
                    }
                }
            }
            \If{$\Ready \neq \varnothing$}
            {
                remove a vertex from \Ready and assign it to a processor\;
            }
        }
        \caption{executing DAG transactions}\label{alg:exec_dag}
    \end{algorithm}

@@

    %\includegraphics[width=17cm]{../img/Alg2s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{Txns}{$T$}\SetKwData{Gd}{$G_d=(V_d,E_d)$}
        \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
        \Input{The memory dependency graph \Gd of a transaction set \Txns\\A proper coloring of $G_d$}
        \Output{An execution dag $G_e=(V_e,E_e)$ for the transaction set \Txns}
        \BlankLine
        $V_e \gets V_d$\;
        $E_e \gets \varnothing$\;
        define a total order on colors of $G_d$\;
        \For{each edge $\{u,v\} \in E_d$}
        {
            \eIf{$color[u] < color[v]$}
            {
                $E_e \gets E_e \cup (u,v)$\;
            }{
                $E_e \gets E_e \cup (v,u)$\;
            }
        }
        \caption{Constructing an execution DAG}\label{alg:gen_dag}
    \end{algorithm}

@@

    This problem can be easily solved by using a concurrent counter for storing the balance of this type of
    accounts. A concurrent counter is a data structure which improves concurrency by using multiple memory locations for
    storing a single counter. The value of the concurrent counter is equal to the sum of its sub counters and it can
    be incremented or decremented by incrementing/decrementing any of the sub counters. This way, a concurrent
    counter trades concurrency with memory usage.

    A pseudocode for implementing a concurrent counter which returns an error when the value of the counter
    becomes negative, follows:

    %\includegraphics[width=17cm]{../img/Alg3s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{CC}{Counter}
        \SetKwFunction{Inc}{Increment}\SetKwFunction{Dec}{Decrement}\SetKwFunction{AtomInc}{AtomicIncrement}
        \SetKwFunction{AtomDec}{AtomicDecrement}\SetKwFunction{AtomSet}{AtomicSet}
        \SetKwProg{Fn}{Function}{}{}
        \BlankLine
        \Fn{\Inc{\CC, value, seed}}
        {
            $i \gets seed \bmod \CC.size$\;
           \AtomInc{$\CC.cell[i]$, value}\;
        }
        \BlankLine
        \Fn{\Dec{\CC, value, seed, attempt}}
        {
            \If {attempt = \CC.size}
            {
                restore \CC by adding back the subtracted value\;
                \KwRet{Error}\;
            }
            $i \gets seed \bmod \CC.size$\;
            $i \gets (i + attempt) \bmod \CC.size$\;
            \eIf {$\CC.cell[i] \geq value$}
            {
                \AtomDec{$\CC.cell[i]$, value}\;
            }{
                $r \gets value - \CC.cell[i]$\;
                \AtomSet{$\CC.cell[i]$, $0$}\;
                \Dec{\CC, r, seed, $attempt + 1$}\;
            }
        }
        \caption{Concurrent counter}\label{alg:CC}
    \end{algorithm}

@@

    %\includegraphics[width=17cm]{../img/Alg4s.png}
    \begin{algorithm}
        \DontPrintSemicolon
        \SetKwData{V}{$v_0$}\SetKwData{Graph}{$G_e$}\SetKwData{Chunk}{$C_k$}\SetKwData{Txns}{$T$}
        \SetKwFunction{RPrune}{RecursivePrune}
        \SetKwProg{Fn}{Function}{}{}
        \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
        \Input{An execution dag and a memory chunk \Chunk}
        \Output{The pruned execution dag based on \Chunk}
        \BlankLine
        \For{each vertex \V with out degree $0$}
        {
            \RPrune{\V}\;
        }
        \BlankLine
        \Fn{\RPrune{\V}}
        {
            \If{$Adj[\V] = \varnothing$ {\bf and} \V does not modify \Chunk}
            {
                remove \V from \Graph\;
                \For{each $u$ such that $\V \in Adj[u]$}
                {
                    \RPrune{u}\;
                }
            }
        }
        \caption{Pruning the execution DAG}\label{alg:prune_dag}
    \end{algorithm}
